---
title: "Covid91 vaccine study Final2021"
author: "Denise Sahagun!"
date: "May 2021"
output: 
  html_document:
    number_sections: true
    toc: true

---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups consisting of Males, Females, just the drug users, and just those in the LGBTQ community. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.


# Males 

```{r}
maledata<- filter(FinalData,sex=="guy")
maledata$sex <- as.factor(maledata$sex)
maledata$treatment <- as.factor(maledata$treatment)
```

## Bar chart 

```{r}
Male <- maledata %>% group_by(treatment,infected) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())
```

I didn't know how to fix error that kept trying it multiple times. I did watch the videos and seen the different plots. 
I had to delete lines "basicC <- ggplot(males,aes(x=treatment,y=count,fill=infected))
basicC + geom_bar(stat="identity",position="dodge")

basicCC <- ggplot(treatment,aes(x=sex,y=prcnt*100,fill=infected)) 
basicCC + geom_bar(stat="identity", position = "dodge", to be able to knit the project.


The bar chart showed 340 people were infected with Covid, around 50% (males) percent were given the drug. 40% (males) of infected males received the placebo.

## Nummerical summary 


```{r}
table1 <- xtabs(~treatment + infected, data=maledata)
rowPerc(table1)
colPerc(table1)
print (table1)
```

As seen on the table above there were thousands of males involved in the study and out of all those people 340 males became infected with Covid. it also shows the percentages of who got the drug and the placebo.

## Inferential 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The table above shows the the extremely small p value.
$H_0$ The null hypothesis is that there is no real difference if the male vaccine get the vaccine or not.
$H_A$The alternative hypothesis is the vaccine would make a difference in weather of not the male gets Covid.

The vaccines efficacy of the drug is retrieved by dviding the odd ratio of 1.47:1 by 0/(1+0)*100 which will get you 59.5. Therefore the Efficacy of the vaccine is 59.5%
  

#Females 

```{r}
femaledata<- filter(FinalData,sex=="gal")
femaledata$sex <- as.factor(femaledata$sex)
femaledata$treatment <- as.factor(femaledata$treatment)
```


## Bar chart 

```{r}
Females <- Femaledata %>% group_by(infected, treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(Females,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(Females,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


#LGBTQ


#Drugusers 


